---
title: 'Kobe Bryant Shot Selection'
author: "ooDoo"
date: "2017년 2월 16일"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# basic package
library(ggplot2)
library(ggthemr)
library(dplyr)
library(data.table)
library(lubridate)
library(readr)

#setwd
knitr::opts_knit$set(root.dir = "C:/Users/LG/Desktop/R/3. DATA/DATA_ML/Kobe")
```


#1. DATA IMPORT
```{r}
Kobe <- read_csv("data.csv")
head(Kobe)
summary(Kobe)
```

##1-1) DATA SPLIT BY train_kobe & test_kobe
```{r}
train_kobe <- Kobe[!is.na(Kobe$shot_made_flag), ]
test_kobe <- Kobe[is.na(Kobe$shot_made_flag), ]
```



#2. DATA EXPLORATION
##2-1) COLUM EXPLANATION
```{r}
names(train_kobe)
# shot type
sort(unique(train_kobe$action_type)) #55EA
unique(train_kobe$combined_shot_type) # 6EA
# remain time
unique(train_kobe$minutes_remaining) # left seconds before to finish quater
unique(train_kobe$seconds_remaining) # left seconds before to finish quater
# shot distance and area zone
unique(train_kobe$shot_distance) 
unique(train_kobe$shot_zone_range)
unique(train_kobe$shot_zone_area) # divide floor to 6th zone.
unique(train_kobe$shot_zone_basic) 

# stadium location
"unique(train_kobe$lat)"
"unique(train_kobe$lon)"
# court location
"unique(train_kobe$loc_x)"
"unique(train_kobe$loc_y)"
# LA lakers
unique(train_kobe$team_id)
unique(train_kobe$team_name)
head(unique(train_kobe$game_date))
# playoffs
unique(train_kobe$playoffs) # dummy
# etc
unique(train_kobe$period) # quater
unique(train_kobe$season) 
```
##

##2-2) VISUALIZATION 
###(0) Made ~ combined_shot_type
```{r}

train_kobe%>%
    dplyr::select(shot_made_flag, combined_shot_type)%>%
    group_by(combined_shot_type, shot_made_flag) %>%
    summarise(Full_Count = n()) %>%
    arrange(combined_shot_type) %>%
    mutate(Shot_pct = round(Full_Count/sum(Full_Count), digits=3)) %>%
    filter(shot_made_flag == 1) %>%
    ggplot(aes(x = combined_shot_type, y = Shot_pct, fill = combined_shot_type)) +
    geom_col() +
    geom_text(aes(label = Shot_pct),size=4) 

```

###(1) Dunk & No Dunk
```{r}
## Dunk
train_kobe%>%
    filter(combined_shot_type == "Dunk")%>%
    group_by(action_type, shot_made_flag)%>%
    summarise(count = n()) %>%
    mutate(made = (shot_made_flag * count)/sum(count)) %>%
    filter(shot_made_flag == 1) %>%
    ggplot(aes(x = action_type, y = made, fill = action_type)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1 ,hjust = 1))
## No-Dunk
train_kobe%>%
    filter(combined_shot_type != "Dunk")%>%
    group_by(combined_shot_type, shot_made_flag)%>%
    summarise(count = n()) %>%
    mutate(made = (shot_made_flag * count)/sum(count)) %>%
    filter(shot_made_flag == 1) %>%
    ggplot(aes(x = combined_shot_type, y = made, fill = combined_shot_type)) +
    geom_col()
```
*Divide data as Dunk and No-Dunk*
###

   
###(2) Distance~combined_shot_type
```{r}
for(i in 1:6 ){
    train_kobe%>%
    filter(combined_shot_type == unique(train_kobe$combined_shot_type)[i]) %>%
    group_by(shot_distance, combined_shot_type, shot_made_flag) %>%
    summarise(count = n())%>%
    mutate(made = (shot_made_flag * count)/sum(count))%>%
    filter(shot_made_flag == 1) %>%
    ggplot(aes(x = shot_distance, y = made)) +
    geom_col(fill = "steelblue") +
    ggtitle(unique(train_kobe$combined_shot_type)[i]) +
    theme(plot.title = element_text(hjust = 0.5))-> k
    assign(paste0("VIS_",i), k)
}
library(gridExtra)
grid.arrange(VIS_1,VIS_2,VIS_3,VIS_4,VIS_5,VIS_6, ncol = 3)
```
*Divide distance !*
"0~2 # dunk and layup
3~5 # all
7~  # shot"
###


###(3) Range~combined_shot_type
```{r}
for(i in 1:6 ){
    train_kobe%>%
    filter(combined_shot_type == unique(train_kobe$combined_shot_type)[i]) %>%
    group_by(shot_zone_range, combined_shot_type, shot_made_flag) %>%
    summarise(count = n())%>%
    mutate(made = (shot_made_flag * count)/sum(count))%>%
    filter(shot_made_flag == 1) %>%
    ggplot(aes(x = shot_zone_range, y = made)) +
    geom_col(fill = "steelblue") +
    ggtitle(unique(train_kobe$combined_shot_type)[i]) +
    theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1 ,hjust = 1),  
          plot.title = element_text(hjust = 0.5)) -> k
    assign(paste0("VIS_",i), k)
}
grid.arrange(VIS_1,VIS_2,VIS_3, ncol = 3)  
grid.arrange(VIS_4,VIS_5,VIS_6, ncol = 3)
```
###

###(4) shot_zone_area ~ shot_type
```{r}
for(i in 1:6 ){
    train_kobe%>%
    filter(combined_shot_type == unique(train_kobe$combined_shot_type)[i]) %>%
    group_by(shot_zone_area, combined_shot_type, shot_made_flag) %>%
    summarise(count = n())%>%
    mutate(made = (shot_made_flag * count)/sum(count))%>%
    filter(shot_made_flag == 1) %>%
    ggplot(aes(x = shot_zone_area, y = made, fill = shot_zone_area)) +
    geom_col() +
    ggtitle(unique(train_kobe$combined_shot_type)[i]) +
    theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1 ,hjust = 1), 
          plot.title = element_text(hjust = 0.5)) +
    guides(fill=FALSE) -> k
    
    assign(paste0("VIS_",i), k)
}
grid.arrange(VIS_1,VIS_2,VIS_3, ncol = 3)  
grid.arrange(VIS_4,VIS_5,VIS_6, ncol = 3)
```
###

###(5) period ~ shot made
```{r}
train_kobe%>%
    filter(playoffs == 1)%>%
    group_by(period, shot_made_flag)%>%
    summarise(made = n())%>%
    mutate(full_count = sum(made), prop = made/full_count)%>%
    filter(shot_made_flag == 1)%>%
    ggplot(aes(x = period, y = prop)) +
    geom_col(fill = "hotpink") +
    ggtitle("Playoff") + 
    theme(plot.title = element_text(hjust = 0.5)) -> g1
train_kobe%>%
    filter(playoffs == 0)%>%
    group_by(period, shot_made_flag)%>%
    summarise(made = n())%>%
    mutate(full_count = sum(made), prop = made/full_count)%>%
    filter(shot_made_flag == 1)%>%
    ggplot(aes(x = period, y = prop)) +
    geom_col(fill = "deepskyblue") +
    ggtitle("Season") +
    theme(plot.title = element_text(hjust = 0.5)) -> g2
grid.arrange(g1,g2, ncol = 2)
```
###

###(6) time_remaining ~ made
```{r}
train_kobe%>%
    group_by(seconds_remaining, shot_made_flag)%>%
    summarise(made = n())%>%
    mutate(full_count = sum(made), prop = made/full_count)%>%
    filter(shot_made_flag == 1)%>%
    ggplot(aes(x = seconds_remaining, y = prop)) +
    geom_col(fill = "hotpink") +
    ggtitle("Seconds_remaining") +
    theme(plot.title = element_text(hjust = 0.5)) -> g1
train_kobe%>%
    group_by(minutes_remaining, shot_made_flag)%>%
    summarise(made = n())%>%
    mutate(full_count = sum(made), prop = made/full_count)%>%
    filter(shot_made_flag == 1)%>%
    ggplot(aes(x = minutes_remaining, y = prop)) +
    geom_col(fill = "deepskyblue") +
    ggtitle("Minutes_remaining") +
    theme(plot.title = element_text(hjust = 0.5)) -> g2
grid.arrange(g1,g2,ncol = 2)
```
###


###(7) season~made & throw
```{r}
train_kobe%>%
    group_by(season, shot_made_flag)%>%
    summarise(made = n()) %>%
    mutate(full_count = sum(made), prop = made/full_count)%>%
    filter(shot_made_flag == 1) %>%
    ggplot(aes(x = season, y = full_count, fill = prop)) +
    geom_col() +
    scale_fill_gradient(low="firebrick1", high="deepskyblue") +
    theme(axis.text.x = element_text(angle = 45)) 
```
###


###(8) Court _ source[How to create NBA shot charts in R]
```{r}
# basic Chart
for(i in 1:length(unique(train_kobe$season))){
    train_kobe%>%
        filter(loc_y <= 400) %>%
        filter(season == unique(train_kobe$season)[i]) %>%
        ggplot(aes(x = loc_x, y = loc_y)) +
        geom_point(aes(colour = factor(shot_made_flag))) +
        ggtitle(paste0("season",i,"_shot distribution")) +
        theme(legend.title=element_blank())-> k
    
    assign(paste0("VIS_",i), k)
}
grid.arrange(VIS_1,VIS_2,VIS_3,VIS_4, ncol = 2)
grid.arrange(VIS_17,VIS_18,VIS_19,VIS_20, ncol = 2)
```

```{r}
# Shot Charts
library(grid)
library(jpeg)
# half court image 
court <- rasterGrob(readJPEG("nba_court.jpg"),width=unit(1,"npc"),height=unit(1,"npc"))
# plot using NBA court background and colour by shot zone 
for(i in 1:length(unique(train_kobe$season))){
    train_kobe%>%
        filter(season == unique(train_kobe$season)[i],
               loc_y <= 400 ) %>%
        ggplot(aes(x = loc_x, y = loc_y)) +
        annotation_custom(court, -250,250,-50,420) +
        geom_point(aes(colour = shot_zone_basic, shape = factor(shot_made_flag)), alpha = 0.8 ) +
        xlim(250, -250) + ylim(-50, 420) +
        geom_rug(alpha = 0.2) + # to see the density
        coord_fixed() +   # coordinate the court.  
        ggtitle(paste0("season",i,"_shot distribution")) +
        theme(line = element_blank(), plot.title = element_text(hjust = 0.5),
             axis.title.x = element_blank(), axis.title.y = element_blank(),
             axis.text.x = element_blank(), axis.text.y = element_blank()) -> k
    assign(paste0("VIS_",i), k)
}
VIS_14
VIS_18
VIS_20
```

```{r}
train_kobe%>%
    filter(loc_y >= 400) %>%
    group_by(shot_made_flag)%>%
    summarise(count = n())
```
*remove outlier shot which over 400 loc y *

```{r}
for(i in 1:length(unique(train_kobe$season))){
    train_kobe%>%
        filter(season == unique(train_kobe$season)[i],
               loc_y <= 400 ) %>%
        ggplot(aes(x = loc_x, y = loc_y)) +
        annotation_custom(court, -250,250,-50,420) +
        geom_point(aes(colour = factor(shot_made_flag)), alpha = 0.8 ) +
        xlim(250, -250) + ylim(-50, 420) +
        geom_rug(alpha = 0.2) + # to see the density
        coord_fixed() +  # coordinate the court.
        ggtitle(paste0("season",i,"_shot distribution")) +
        theme(line = element_blank(), plot.title = element_text(hjust = 0.5),
             axis.title.x = element_blank(), axis.title.y = element_blank(),
             axis.text.x = element_blank(), axis.text.y = element_blank()) -> k
    
    assign(paste0("VIS_",i), k)
}
VIS_14
VIS_18
VIS_20
```
###
##
#


#3. FEATURE HANDLING
##3-1)FEATURE EXTRACT
```{r}
names(train_kobe)
```

```{r}
EAST <- c("BKN", "BOS", "ATL", "ORL", "WAS", "CHA", "NYK", "CLE", "DET", "CHI", "TOR", "IND", "MIL", "PHI", "MIA")
```
```{r}
FeatureExtract <- function(data){
    data%>%
        # FACTOR
        mutate(season = factor(season),
               shot_type = factor(shot_type),
               action_type = factor(action_type),
               combined_shot_type = factor(combined_shot_type),
               shot_zone_area = factor(shot_zone_area),
               shot_zone_basic = factor(shot_zone_basic),
               shot_zone_basic = factor(shot_zone_range))%>%
               
        # month & season_divide
        mutate(month = month(game_date),
               season_divide = ifelse(month == 10 | month == 11 | month == 12, "season_early",
                                    ifelse(month == 1 | month == 2 | month == 3,"season_mid",
                                        ifelse(month == 4 | month == 5 | month == 6,  "season_late", NA)))) %>%
        
        # time, clutch, slump_season
        mutate(time = (minutes_remaining * 60 + seconds_remaining),
               clutch = ifelse(time <= 5 & period >=4, 1, 0), 
               slump_season = ifelse(season == "2013-14" , 1, 
                                ifelse(season == "2014-15", 1,
                                    ifelse(season == "2015-16" , 1, 0)))) %>%
        
        # Conference & Division
        #mutate(opponent = as.character(opponent)) %>%
        #mutate_each(funs(conference = if_else(opponent%in% EAST == TRUE, 0, 1)), opponent) %>%
        
        # DELETE UNNECESSARY COLUMS
        dplyr::select(-c(game_event_id, game_id, lat, lon, team_name, team_id, game_date, minutes_remaining, seconds_remaining, shot_id))
}
```

```{r}
# Apply FeatureExtract
train_kobe_N <- FeatureExtract(train_kobe) 
test_kobe_N <- FeatureExtract(test_kobe) #test_kobe_N's nrow  4,989
```

```{r}
#  home_away
splitString <- function(data){
    strsplit(data, split = "[@]")[[1]][2]
}
    train_kobe_N$matchup <- as.character(train_kobe_N$matchup)
    train_kobe_N$home_away <- sapply(train_kobe_N$matchup, FUN = splitString)
    train_kobe_N$home_away <- ifelse(is.na(train_kobe_N$home_away) == TRUE, 1, 0)
    train_kobe_N$matchup <- NULL
    
    test_kobe_N$matchup <- as.character(test_kobe_N$matchup)
    test_kobe_N$home_away <- sapply(test_kobe_N$matchup, FUN = splitString)
    test_kobe_N$home_away <- ifelse(is.na(test_kobe_N$home_away) == TRUE, 1, 0)
    test_kobe_N$matchup <- NULL
```

##3-2) OUTLIER DELETE
```{r}
#train_kobe_N%>%
#    filter(loc_y <= 400) -> train_kobe_N
# Be cautious to Do not apply to test data! 
```



#4.FEATURE SELECT[boruta]
##4-1) BORUTA
*[Boruta]function : Boruta(data, target value, maxRuns = n)*
```{r}
names(train_kobe_N)
```

```{r}
library(Boruta)
set.seed(123)
bor.result <- Boruta(train_kobe_N[,-9], train_kobe_N[,9], maxRuns = 11)
```
##

##4-2) RESULT 
```{r}
# resulst
bor.result
bor.result$finalDecision
head(bor.result$ImpHistory)
```

##4-3) VIS IMPORTANCE FEATURE
```{r}
# basic plot using [plot]
plot(bor.result)
# custom plot using [ggplot] 
library(reshape2)
data.frame(bor.result$ImpHistory)%>%
    melt(variable.name = "Feature" ,value.name = "importance") %>%
    group_by(Feature) %>%
    mutate(Feature_mean = mean(importance)) %>%
    arrange(Feature_mean) %>%
    ungroup(Feature) %>%
    mutate(Feature = as.vector(Feature)) %>%
    mutate(Feature = factor(Feature, levels=unique(Feature))) %>%
    mutate(level = ifelse(Feature_mean > 4.9, "Good", 
                        ifelse(Feature_mean < 4.8 & Feature_mean > 2, "Not good",
                            ifelse(Feature_mean <2, "Bad", NA)))) %>%
    ggplot(aes(x = Feature, y = importance, fill = factor(level))) +
    geom_boxplot() +
    theme(axis.text.x = element_text(angle = 55, hjust=1, vjust=1)) +
    scale_fill_discrete(breaks=c("Good","Not good","Bad"))
```
#


#5. ONE-HOT ENCODING
##5-1) MATRIX [ORIGINAL DATA]
```{r}
# data
train_kobe_mat <- model.matrix(shot_made_flag ~ 0 + . , train_kobe_N)[, -1]
head(train_kobe_mat)
test_kobe_N <- dplyr::select(test_kobe_N, -shot_made_flag)
test_kobe_mat <- model.matrix( ~ 0 + . , test_kobe_N)[, -1] # i don't know why but, when if i don't delete NA column, it make list not matirx
# label
train_kobe_label <- train_kobe_N[,"shot_made_flag"]
```
##
#

#6. XGB
##6-1) PARAMETER SEARCHING
```{r}
library(xgboost)
params <- list(eta = 0.05,
               max.depth = 5,
               gamma = 0,
               colsample_bytree = 1,
               subsample = 1,
               objective = "binary:logistic",
               eval_metric = "logloss")
```

##6-2) RUN Cross Validation 
```{r}
set.seed(1234)
xgbcv <- xgb.cv(params = params,
                nrounds = 200,
                nfold = 10,
                metrics = "logloss",
                data = train_kobe_mat,
                label = train_kobe_label,  
                verbose = 0)
```

##6-3) CHECK BEST ITER VALUE
```{r}
xgb.best <- arrange(xgbcv$evaluation_log, test_logloss_mean)[1, ] 
xgb.best
```
    
##6-4) REMODELING
```{r}
kobe_xgboost <- xgboost(param =params,
                        data = train_kobe_mat,
                        label = train_kobe_label,
                        nrounds = xgb.best$iter,
                        verbose = 1
                        )
```

```{r}
kobe_xgb_pred <- predict(kobe_xgboost, test_kobe_mat)
```

##6-5) SUBMISSION
```{r}
submission <- data.frame(shot_id = test_kobe$shot_id,
                         shot_made_flag = kobe_xgb_pred)
write.csv(submission, "C:/Users/LG/Desktop/kobe_xgb_ooDoo_5.csv" , row.names = FALSE)
```



#7. Dunk & No-Dunk
##7-1) DATA SPLIT BY Dunk & No-Dunk 
```{r}
train_kobe_N%>%
    filter(combined_shot_type == "Dunk") -> train_kobe_Dunk 
train_kobe_N%>%
    filter(combined_shot_type != "Dunk") -> train_kobe_No_Dunk 

test_kobe_N%>%
    filter(combined_shot_type == "Dunk") -> test_kobe_Dunk 
test_kobe_N%>%
    filter(combined_shot_type != "Dunk") -> test_kobe_No_Dunk 

# for shot_id
test_kobe%>%
    filter(combined_shot_type == "Dunk")%>%
    dplyr::select(shot_id) -> test_kobe_Dunk_shotId
test_kobe%>%
    filter(combined_shot_type != "Dunk")%>%
    dplyr::select(shot_id) -> test_kobe_No_Dunk_shotId
```

##7-2) ONE-HOT ENCODING
```{r}
# matrix
train_kobe_Dunk_mat <- model.matrix(shot_made_flag ~ 0 + . , train_kobe_Dunk )[, -1]
train_kobe_No_Dunk_mat <- model.matrix(shot_made_flag ~ 0 + . , train_kobe_No_Dunk )[, -1]

test_kobe_Dunk_mat <- model.matrix( ~ 0 + . , test_kobe_Dunk)[, -1]
test_kobe_No_Dunk_mat <- model.matrix( ~ 0 + . , test_kobe_No_Dunk)[, -1] 

# label
train_kobe_Dunk_label <- train_kobe_Dunk[,"shot_made_flag"]
train_kobe_No_Dunk_label <- train_kobe_No_Dunk[,"shot_made_flag"]
```
##

##7-3) XGB
###(1) Dunk
```{r}
###(1) PARAMETER SEARCHING
params <- list(eta = 0.05,
               max.depth = 5,
               gamma = 0,
               colsample_bytree = 1,
               subsample = 1,
               objective = "binary:logistic",
               eval_metric = "logloss")

###(2) RUN Cross Validation 
set.seed(1234)
xgbcv <- xgb.cv(params = params,
                nrounds = 200,
                nfold = 10,
                metrics = "logloss",
                data = train_kobe_Dunk_mat,
                label = train_kobe_Dunk_label,  
                verbose = 0)  #alpha = like lasso, it will remove unnecessary column

###(3) CHECK BEST ITER VALUE
xgb.best <- arrange(xgbcv$evaluation_log, test_logloss_mean)[1, ] 
xgb.best

###(4) REMODELING
kobe_xgboost <- xgboost(param =params,
                        data = train_kobe_Dunk_mat,
                        label = train_kobe_Dunk_label,
                        nrounds = xgb.best$iter,
                        verbose = 1
                        )
###(5) PREDICT
kobe_xgb_pred_Dunk <- predict(kobe_xgboost, test_kobe_Dunk_mat)
kobe_xgb_pred_Dunk_DF <- data.frame(shot_id = test_kobe_Dunk_shotId$shot_id,
                                    shot_made_flag = kobe_xgb_pred_Dunk)
```

###(2) No-Dunk
```{r}
###(1) PARAMETER SEARCHING
params <- list(eta = 0.05,
               max.depth = 5,
               gamma = 0,
               colsample_bytree = 1,
               subsample = 1,
               objective = "binary:logistic",
               eval_metric = "logloss")

###(2) RUN Cross Validation 
set.seed(1234)
xgbcv <- xgb.cv(params = params,
                nrounds = 200,
                nfold = 10,
                metrics = "logloss",
                data = train_kobe_No_Dunk_mat,
                label = train_kobe_No_Dunk_label,  
                verbose = 0)

###(3) CHECK BEST ITER VALUE
xgb.best <- arrange(xgbcv$evaluation_log, test_logloss_mean)[1, ] 
xgb.best

###(4) REMODELING
kobe_xgboost <- xgboost(param =params,
                        data = train_kobe_No_Dunk_mat,
                        label = train_kobe_No_Dunk_label,
                        nrounds = xgb.best$iter,
                        verbose = 1
                        )
###(5) PREDICT
kobe_xgb_pred_No_Dunk <- predict(kobe_xgboost, test_kobe_No_Dunk_mat)
kobe_xgb_pred_No_Dunk_DF <- data.frame(shot_id = test_kobe_No_Dunk_shotId$shot_id,
                                       shot_made_flag = kobe_xgb_pred_No_Dunk)

```

###(3)rbind Dunk and No Dunk
```{r}
submission_Dunk_NoDunk <- rbind(kobe_xgb_pred_Dunk_DF, kobe_xgb_pred_No_Dunk_DF)
submission_Dunk_NoDunk%>%
    arrange(shot_id) -> submission_Dunk_NoDunk

write.csv(submission_Dunk_NoDunk, "C:/Users/LG/Desktop/kobe_xgb_ooDoo_DND_6.csv" , row.names = FALSE)
```



#8. Logistic
##8-1) SET LOGIT MODEL
```{r}
#  motion_type
splitString <- function(x){
    strsplit(x, split = '[ ]')[[1]][1]
}
    train_kobe_N$action_type <- as.character(train_kobe_N$action_type)
    train_kobe_N$motion_type <- sapply(train_kobe_N$action_type, FUN = splitString)
    train_kobe_N$action_type <- as.factor(train_kobe_N$action_type)

    test_kobe_N$action_type <- as.character(test_kobe_N$action_type)
    test_kobe_N$motion_type <- sapply(test_kobe_N$action_type, FUN = splitString)
    test_kobe_N$action_type <- as.factor(test_kobe_N$action_type)
```


```{r}
kobe_logit <- glm(shot_made_flag~ combined_shot_type + loc_x + loc_y + period + playoffs + season + shot_distance + shot_type + shot_zone_area + shot_zone_basic + shot_zone_range + opponent + home_away + motion_type, data = train_kobe_N, family = "binomial")
# use motion_type varibale instead action_type, since test's action_type has no some index 
```

##8-2) PREDICT
```{r}
kobe_logit_pred <- predict(kobe_logit, test_kobe_N, type = "response") # [type = "response"] for prop value
submission <- data.frame(shot_id = test_kobe$shot_id,
                         shot_made_flag = kobe_logit_pred)
write.csv(submission, "C:/Users/LG/Desktop/kobe_logit_ooDoo_1.csv" , row.names = FALSE)
```






#9. RESULT VIS
```{r}
RESULT_DF <- data.frame(file_name = c("kobe_xgb_ooDoo_1", "kobe_xgb_ooDoo_2","kobe_xgb_ooDoo_3", "kobe_xgb_ooDoo_DND", "kobe_xgb_ooDoo_DND_2", "kobe_xgb_ooDoo_DND_3", "kobe_logit_ooDoo_1" ),
                        file_describe = c("XGB_Vanila", "NoOpponent", "parameter_change", "D_ND", "D_ND_2",  "D_ND_3", "logit_vanila" ),
                        eta = c(0.3, 0.3, 0.05, 0.3, 0.05, 0.05, 0),
                        iter = c(30, 32, 192, 32, 198, 271, 0),
                        logloss = c(0.60481, 0.60634, 0.60427, 0.60537, 0.60407, 0.60497, 0.61379)
             )
RESULT_DF%>%
    ggplot(aes(x = file_describe, y = logloss, color = factor(iter), shape = factor(eta))) +
    geom_line(group = 1, color = "black", alpha = 0.5) +
    geom_point(size = 3) +
    geom_vline(xintercept = 2, linetype = "dashed", alpha = 0.5 ) +
    theme(axis.text.x = element_text(angle = 45, face = "italic", vjust = 1 ,hjust = 1))

```